``Software Engineering Is Programming Integrated Over Time''

\bigskip
What stands out the most in this final degree project is the task of designing an application that is user-friendly and easy to use, while still maintaining the power and customization that would be offered by creating a webpage from scratch. That's why, whenever we designed new content for the LMS, we questioned whether it would break the philosophy of always providing a good user experience. If it didn't align with that goal, even if it was a powerful feature, we set it aside to prioritize the user. An example of this was attempting to add an authentication system to the LMS, but it would have made the user configuration more complex. So, even though the idea was good and almost finished, we decided to backtrack.

Although a large part of the work has been challenging due to the various difficulties we encountered while creating the LMS to be the best it could be, we managed to create a system that, although it may seem simple at first glance, always gives the user the opportunity to control the desired outcome to nearly 100%.

This, coupled with the fact that I learned a great number of technologies that I knew nothing or very little about before, has made all the work and effort worthwhile. Sometimes, we get carried away trying to always experiment with new things, but there came a point where we had to set a limit because, despite the joy of learning something new, this project had a set deadline. Nevertheless, the final experiences I gained from it will benefit me in the future, and for that, I am grateful.

The final degree project is completed, but the project can continue to grow as much as desired. This type of project requires constant and prolonged work to gain acceptance among users. My intentions are to continue contributing to this project at some point and treat it as a personal endeavor.